Wind_analyses

### 2019-03-09 Wind_analyses.Rmd
fixed_path

wind_1 <- read.delim("/home/amieroh/Documents/Masters_2019/MastersProject/Data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings="") 
colnames(wind_1) <- c("station_number", "station_name", "date", "hour", "sub", "speed", "dir")

wind_2 <- read.delim("/home/amieroh/Documents/Masters_2019/MastersProject/Data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings="")
colnames(wind_2) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

wind_3 <- read.delim("/home/amieroh/Documents/Masters_2019/MastersProject/Data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings="")
colnames(wind_3) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

>>>>

wind_1 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings="") 
colnames(wind_1) <- c("station_number", "station_name", "date", "hour", "sub", "speed", "dir")

wind_2 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings="")
colnames(wind_2) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

wind_3 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings="")
colnames(wind_3) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")
